Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
Rephrased generic description of experimental process.

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{DSVerifier Verification Flow.}
\label{DSVerifier_process}
\end{figure*}

@@

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ represented by Eq.~\ref{FWL_tf} (step B) to
calculate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it
i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
synthesise.  If any property violation is found, then
a counterexample is reported, which contains system inputs or
parametric deviations $\Delta{G}$ that lead the system to a failure.  
This information allows the CEGIS module to refine its search for a stable
controller, which we explain in detail in section~\ref{synthesiser-general}.
A successful verification result is reported if the system is safe with
respect to $\phi$.  In particular, the stability verification is complete
and sound, since it does not depend on system inputs and outputs.  In the
case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients by
the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
\label{DSVerifier_process}
\end{figure*}

@@

Given a model for a plant for which to synthesize a controller,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and a transfer
function $f$ represented by Eq.~\ref{FWL_tf} (step B) to calculate the parameters
of the controller to be synthesized (step C).  Finally DSVerifier builds an
intermediate ANSI-C code for the digital system implementation, which is used as
input for the controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
(CEGIS) module, where the controller is marked as input variable to synthesize.
The properties specified in the ANSI-C code model can only be satisfied if CEGIS
synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
counterexample-guided refinement process which is explained in detail in
section~\ref{synthesiser-general}. A successful synthesis result is reported if
CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
the ANSI-C code model guarantees that a synthesized solution is complete
and sound with respect to stability property $\phi$, since it does not depend on
system inputs and outputs.  In the case of stability, the specification $\phi$
consists in a number of assumptions on the polynomial coefficients, following
Jury's Criteria, as well as the restrictions set in the representation of these
coefficients by the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
